IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-10 codes/R/cohorts_nc.Rnw
change _ to . in social class labels to avoid plot conflicts in latex

% 
% <<COUNTERF, dependson="FA_SCORES_MAIN">>=
% # perform counterfactuals
% @
% 
% <<COUNTERF_PREP_PLOTS, dependson='COUNTERF'>>=
% # prepare counterfactual plots
% @
% 
% \begin{landscape}
% \begin{figure}
% <<COUNTERF_EXT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
% cfp.ext
% @
% \caption{Counterfactual decomposition -- externalising skills}\label{fig:counterf}
% {\scriptsize \emph{Notes}: \par}
% \end{figure}
% \end{landscape}
% 
% \begin{landscape}
% \begin{figure}
% <<COUNTERF_INT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
% cfp.int
% @
% \caption{Counterfactual decomposition -- internalising skills}\label{fig:counterf}
% {\scriptsize \emph{Notes}: \par}
% \end{figure}
% \end{landscape}

>>>>

<<COUNTERF, dependson="FA_SCORES_MAIN">>=
# perform counterfactuals
@

<<COUNTERF_PREP_PLOTS, dependson='COUNTERF'>>=
# prepare counterfactual plots
@

\begin{landscape}
\begin{figure}
<<COUNTERF_EXT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.ext
@
\caption{Counterfactual decomposition -- externalising skills}\label{fig:counterf_ext}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
<<COUNTERF_INT, dependson='COUNTERF_PREP_PLOTS', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.int
@
\caption{Counterfactual decomposition -- internalising skills}\label{fig:counterf_int}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}
